Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-13 paper/manuscript.tex
Very minor adjustments to some sentences in results

\subsection*{For all antibodies, the selected sites of escape occur in the antibody binding footprints}
We visualized for each mutation the fraction surviving selection as a logoplot, and mapped the mutation with the maximum fraction surviving selection at each site onto the HA structure, shown in Figure~\ref{fig:structures}.

>>>>

\subsection*{For all antibodies, the selected sites of escape occur in the antibody binding footprints}
We visualized for each mutation the fraction surviving selection as a logoplot, and for each site mapped the mutation with the maximum fraction surviving selection onto the HA structure, shown in Figure~\ref{fig:structures}. 
For all of the antibodies, the sites with mutations exhibiting the greatest fraction escape localize in the antibody-binding footprint.
